Lyman-alpha spectra from rotating outflows

### 2018-03-26 paper/paper.tex
ready line stats and muse

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/mean_line_7}
	\end{center}
	\caption{\textbf{Mean line for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:mean_line}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/standard_deviation_7}
	\end{center}
	\caption{\textbf{Standard Deviation for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/skewness_7}
	\end{center}
	\caption{\textbf{Skewness for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:skewness}}
\end{figure*}

@@

In addition to this, we also evaluate the effects of the viewing angle
for fixed rotational and outflows velocity. We measure the intensity of the 
valley between peaks, for each $\theta$ and \tauh. Figure \ref{fig:valley_intensity} 
summarizes the information with all plots corresponding to the same outflow
velocity of $\vout=75$\kms and rotation velocity of $\vrot=50$\kms.

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/valley_intensity}
	\end{center}
	\caption{\textbf{Caption:} We fixed $\vout=75$\kms and $\vrot=50$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

@@

\subsection{Theoretical Insights}
\color{red}
Why Doppler Shift works. Talk about radiative transfer...
\color{black}
In Fig. \ref{fig:doppler} we present the spectrum pf a LAE taken from to different sides of the galaxy. As the LAE is rotating, one side is being redshifted while the other is blueshifted. We see that the combined spectrum is a weighted line, in black, that combines these past two. This shows that there is in effect a Doppler Shift and justifies our choice to apply it after the outflows spectrum is obtained.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.55\textwidth]{./figures/discussion/doppler}
	\end{center}
	\caption{\textbf{Caption:} $\vout=25$\kms, $\vrot=100$\kms, $\tauh=10^5$.
		\label{fig:doppler}}
\end{figure*}

>>>>

\begin{figure}
	\begin{center}
		\includegraphics[height=0.1\textheight]{./figures/results/line_characterization_mn_vout5_logtau7}
		\includegraphics[height=0.1\textheight]{./figures/results/line_characterization_mn_vout25_logtau7}
		\includegraphics[height=0.1\textheight]{./figures/results/line_characterization_mn_vout50_logtau7}
	\end{center}
	\caption{\textbf{Mean line for RT and DS:} The triangles represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:mean_line}}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[height=0.11\textheight]{./figures/results/line_characterization_std_vout5_logtau7}
		\includegraphics[height=0.11\textheight]{./figures/results/line_characterization_std_vout25_logtau7}
		\includegraphics[height=0.11\textheight]{./figures/results/line_characterization_std_vout50_logtau7}
	\end{center}
	\caption{\textbf{Standard Deviation for RT and DS:} The triangles represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:standard_deviation}}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[height=0.11\textheight]{./figures/results/line_characterization_skw_vout5_logtau7}
		\includegraphics[height=0.11\textheight]{./figures/results/line_characterization_skw_vout25_logtau7}
		\includegraphics[height=0.11\textheight]{./figures/results/line_characterization_skw_vout50_logtau7}
	\end{center}
	\caption{\textbf{Skewness for RT and DS:} The triangles represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:skewness}}
\end{figure}

@@

In addition to this, we also evaluate the effects of the viewing angle
for fixed rotational and outflows velocity. We measure the intensity of the 
valley between peaks, for each $\theta$ and \tauh. Figure \ref{fig:valley_intensity} 
summarizes the information with all plots corresponding to the same outflow
velocity of $\vout=5$\kms and rotation velocity of $\vrot=100$\kms.

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure}
	\begin{center}
		\includegraphics[height=0.12\textheight]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
		\includegraphics[height=0.12\textheight]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
		\includegraphics[height=0.12\textheight]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
	\end{center}
	\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger 
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the 
		higher the valley intensity. We fixed $\vout=5$\kms and $\vrot=100$\kms. 
		\label{fig:valley_intensity}}
\end{figure}

@@

\subsection{Theoretical Insights}
\color{red}
Why Doppler Shift works. Talk about radiative transfer...
\color{black}
In Fig. \ref{fig:doppler} we present the spectrum of a LAE taken from to different 
sides of the galaxy. As the LAE is rotating, one side is being redshifted while 
the other is blueshifted. We see that the combined spectrum is a weighted line, 
in solid black, that combines these past two. This shows that there is in effect a 
Doppler Shift and justifies our choice to apply it after the outflows spectrum is 
obtained.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.45\textwidth]{./figures/discussion/doppler}
	\end{center}
	\caption{\textbf{Doppler Shift:} We fix $\vout=25$\kms, $\vrot=100$\kms, $\tauh=10^5$.
		\label{fig:doppler}}
\end{figure}
